Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments

### 2019-01-09 Journal/JINT 2018/JINT18.tex
added mars presentation

\author{Evan Kaufman \and Kuya Takami \and \\ Zhuming Ai \and Taeyoung Lee}%
%\thanks{Evan Kaufman, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{evankaufman,tylee\}@gwu.edu}}
%\thanks{Zhuming Ai, Ira S. Moskowitz, Information Management \& Decision Architectures, U.S. Naval Research Laboratory,  Washington, DC 20375}
%}

%\authorrunning{Short form of author list} % if too long for running head

@@

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

%Mapping is of fundamental importance for robots to understand their environment, avoid collisions, and efficiently maneuver through their surroundings.
%Several grid-based map representations have been studied, e.g.,~\cite{WolSuk05,MeyBeiBur12,TanThoWolBus14}, because they provide abundant occupancy knowledge about the environment for collision-free maneuvers and are computationally tractable.

@@

%        1.      sensor fusion in mapping
The approximate nature of the occupancy probability, either by a simplified function or a learned solution, motivates an exact Bayesian solution to the inverse sensor model. In this paper, we propose a computationally-efficient algorithm to obtain this solution, which serves to generate probabilities in a 3D environment following the framework of~\cite{KauLeeAiMos16,KauTakAiLee17}. This approach approach integrates stochastic properties of all sensors and the prior map estimate, following a Bayesian framework, to obtain the exact 3D occupancy probabilities~\cite{KauTakAiLee18}. As such, it provides a unified framework for sensor fusion between multiple sensors with various properties, such as sensor accuracy and fields of view.

%        2.      proposing a method to combine 3D mapping and 2D exploration: Also, we need to motivate why we are not doing full 3D exploration. Stress that we are proposing a computationally friendly approach to perform 3D mapping with projection using the fact there is less variation in the floor plan along the vertical direction.
The 3D occupancy grid map provides key information to produce the policies that govern robotic motion, referred to as autonomous exploration. Among several approaches to determine these map-based motions in real-time, the most popular approach is known as frontier-based exploration. Using frontiers for autonomous exploration was proposed for 2D environments in~\cite{Yam97,Yam98} and extended to 3D with a visibility metric in~\cite{SawKriSri09} and~\cite{ZhuDinLinWu15,SenWan16,KleDor13} using the Octomap representation. The main idea of this approach is that robots move toward the boarder between certain and uncertain spaces to push back the boundary of known space. However, these systematic actions are not based on any consideration of the future probabilistic map uncertainty.

@@

%        3.      hardware/software for aerial exploration experiment.
In this paper, we present a flight experiment for the proposed single-vehicle exploration scheme. Multiple tasks, such as flight control, sensor data acquisition, mapping, exploration, and communications are executed simultaneously in a ROS environment using Python/C++. These tasks are verified with a quadrotor unmanned aerial vehicle holding an ASUS Xtion infrared depth sensor and Hokuyo laser scanner operated by the NVidia Jetson computing module.

@@

%In short, there are two contributions of this paper. First, single-vehicle 2D mapping and autonomous exploration approaches are extended to realistic 3D environments. Second, multi-vehicle cooperative patrol is proposed using bidding-based autonomous exploration and map grid cell degradation. These two concepts are demonstrated with an experiment and a simulation.

@@

Suppose a future pose candidate and its associated future measurement scan is $X_c=\braces{x_c,R_c}$ and $Z_c$, respectively, where $c\in\mathcal C$ such that $\mathcal C=\braces{1,2,...,n_c}$ accounts for all $n_c$ candidates under consideration for the next robot pose. The current pose of the robot is \emph{not} $X_c$ in general, so changes to the probabilistic map from $X_c$ can only be predicted. 
This is achieved by considering the expected entropy change of individual measurement rays~\cite{KauAiLee16,KauTakAiLee17}. Removing $X_{1:t}$ and $Z_{1:t}$ for simplicity, the expected entropy for candidate ray $z_c$ is
\begin{align}
\label{eqn:DiscExpEntropyRay}
&\text{E}[H(P(m|x_c,z_{c}))]=\sum_{k=1}^{n_{r}+1}\bigg\{H(P(m|x_c,z_{c,k}))P(z_{c,k}|x_c)\bigg\},
\end{align}
where $z_{c,k}$is distance along measurement ray $z_{c}$ from position $x_c$ to the $k$-th grid cell. The first term in \refeqn{DiscExpEntropyRay}, namely $H(P(m|x_c,z_{c,k}))$, is found with the inverse sensor model \refeqn{RayISMAnswer}--\refeqn{Unnormalized} and grid cell entropy \refeqn{ShannonsEntropyCell}--\refeqn{ShannonsEntropyMap}.
The second term is derived from \refeqn{allEta} with
\begin{align}
\label{eqn:ProbMeas}
P(z_{c,k}|x_c)&=\frac{p(z_{c,k}|x_c)}{\sum_{i=1}^{n_{r}+1}p(z_{c,i}|x_c)}=\frac{\eta_{c,k}^{-1}}{\sum_{i=1}^{n_{r}+1}\eta_{c,i}^{-1}},
\end{align}
where $\eta_{c,k}$ refers to the normalizer based on the measurement $z_{c,k}$.
The expected negative entropy change for candidate pose $X_c$ is equivalently the expected information gain,
\begin{align}
%\label{eqn:objectiveFunOptimized}
%X_c^*&=\argmax_{X_c}{\ \mathcal I(X_c)},
%\\
\label{eqn:expectedInfoGainRay}
\mathcal I(X_c)&=H(P(m|X_{1:t},Z_{1:t}))-\text{E}\left[H(P(m|X_c,Z_c))\right].
\end{align}
Then, we repeat \refeqn{DiscExpEntropyRay} for several sample measurement rays composing scan $Z_c$~\cite{KauAiLee16}.

@@

% EditEK 1: example of 2 sensor measurements fused, starting with "For example, a robot may be equipped..." until the end of the paragraph.

@@

%While auctions proceed, the occupancy grid cell probabilities are degrading according to a continuous-time Markov process. Cell degradation increases the expected information gain, thereby incentivizing robots to revisit regions after some time passes.

%Here, we formulate a cooperative patrol scheme based on a coordinated autonomous exploration with multiple robots using sequential auctions. The first auction is based on the expected information gain presented in the prior section, scaled by travel distance. Once the winner of the first auction is determined, the map for bidding is updated based on the expected measurements of the first robot. The second auction for the remaining robots is determined by the information gain from the revised map that is further scaled by the travel distance and a penalty for collision-avoidance. This process is repeated until all robots are assigned tasks. While auctions proceed, the occupancy grid cell probabilities are degrading according to a continuous-time Markov process. Cell degradation increases the expected information gain, thereby incentivizing robots to revisit regions after some time passes.

@@

%    if x(k) < d
%        f(k) = 0.5*fMax*(1-cos(pi*x(k)/d));
%    else
%        f(k) = fDiff*exp(-1e-2*(x(k)-d)^2)+fFar;
%    end

%Dijkstra's search demonstrates that the distances from each robot to $X_c$ are different in general, so travel times to $X_c$ vary. This motivates a unified approach to account for travel time, which promotes local travel and discourages robots from traversing across the map when possible.

@@

\noindent{\bf Evan Kaufman} received his B.S. degree in Mechanical Engineering from Bucknell University in 2012, and is currently a Ph.D. candidate at The George Washington University in the Mechanical and Aerospace department. His research focusses are in robotic mapping and exploration with range-based sensors, estimation, data association, and flight controls. He has worked on several research projects through the U.S. Air Force Research Laboratory and Naval Research Laboratory.

@@

\noindent{\bf Kuya Takami} is a postdoctoral research fellow at the Department of Mechanical and Aerospace Engineering at the George Washington University. He received his doctoral degree in Mechanical Engineering at Virginia Polytechnic Institute and State University in 2015 specializing in robot perception. His main interests include mobile robot perception and autonomous systems.

>>>>

\author{Evan Kaufman \and Kuya Takami \and \\ Zhuming Ai \and Taeyoung Lee}%

@@

\date{Received: date / Accepted: date}

@@

@@

The approximate nature of the occupancy probability, either by a simplified function or a learned solution, motivates an exact Bayesian solution to the inverse sensor model. In this paper, we propose a computationally-efficient algorithm to obtain this solution, which serves to generate probabilities in a 3D environment following the framework of~\cite{KauLeeAiMos16,KauTakAiLee17}. This approach approach integrates stochastic properties of all sensors and the prior map estimate, following a Bayesian framework, to obtain the exact 3D occupancy probabilities~\cite{KauTakAiLee18}. As such, it provides a unified framework for sensor fusion between multiple sensors with various properties, such as sensor accuracy and fields of view.

The 3D occupancy grid map provides key information to produce the policies that govern robotic motion, referred to as autonomous exploration. Among several approaches to determine these map-based motions in real-time, the most popular approach is known as frontier-based exploration. Using frontiers for autonomous exploration was proposed for 2D environments in~\cite{Yam97,Yam98} and extended to 3D with a visibility metric in~\cite{SawKriSri09} and~\cite{ZhuDinLinWu15,SenWan16,KleDor13} using the Octomap representation. The main idea of this approach is that robots move toward the boarder between certain and uncertain spaces to push back the boundary of known space. However, these systematic actions are not based on any consideration of the future probabilistic map uncertainty.

@@

In this paper, we present a flight experiment for the proposed single-vehicle exploration scheme. Multiple tasks, such as flight control, sensor data acquisition, mapping, exploration, and communications are executed simultaneously in a ROS environment using Python/C++. These tasks are verified with a quadrotor unmanned aerial vehicle holding an ASUS Xtion infrared depth sensor and Hokuyo laser scanner operated by the NVidia Jetson computing module.

@@

@@

Suppose a future pose candidate and its associated future measurement scan is $X_c=\braces{x_c,R_c}$ and $Z_c$, respectively, where $c\in\mathcal C$ such that $\mathcal C=\braces{1,2,...,n_c}$ accounts for all $n_c$ candidates under consideration for the next robot pose. The current pose of the robot is \emph{not} $X_c$ in general, so changes to the probabilistic map from $X_c$ can only be predicted. 
This is achieved by considering the expected entropy change of individual measurement rays~\cite{KauAiLee16,KauTakAiLee17}. Removing $X_{1:t}$ and $Z_{1:t}$ for simplicity, the expected entropy for candidate ray $z_c$ is
\begin{align}
\label{eqn:DiscExpEntropyRay}
&\text{E}[H(P(m|x_c,z_{c}))]=\sum_{k=1}^{n_{r}+1}\bigg\{H(P(m|x_c,z_{c,k}))P(z_{c,k}|x_c)\bigg\},
\end{align}
where $z_{c,k}$is distance along measurement ray $z_{c}$ from position $x_c$ to the $k$-th grid cell. The first term in \refeqn{DiscExpEntropyRay}, namely $H(P(m|x_c,z_{c,k}))$, is found with the inverse sensor model \refeqn{RayISMAnswer}--\refeqn{Unnormalized} and grid cell entropy \refeqn{ShannonsEntropyCell}--\refeqn{ShannonsEntropyMap}.
The second term is derived from \refeqn{allEta} with
\begin{align}
\label{eqn:ProbMeas}
P(z_{c,k}|x_c)&=\frac{p(z_{c,k}|x_c)}{\sum_{i=1}^{n_{r}+1}p(z_{c,i}|x_c)}=\frac{\eta_{c,k}^{-1}}{\sum_{i=1}^{n_{r}+1}\eta_{c,i}^{-1}},
\end{align}
where $\eta_{c,k}$ refers to the normalizer based on the measurement $z_{c,k}$.
The expected negative entropy change for candidate pose $X_c$ is equivalently the expected information gain,
\begin{align}
\label{eqn:expectedInfoGainRay}
\mathcal I(X_c)&=H(P(m|X_{1:t},Z_{1:t}))-\text{E}\left[H(P(m|X_c,Z_c))\right].
\end{align}
Then, we repeat \refeqn{DiscExpEntropyRay} for several sample measurement rays composing scan $Z_c$~\cite{KauAiLee16}.

@@

@@

@@

@@

\noindent{\bf Evan Kaufman} is a robotics engineer at Robotic Research LLC. He received his B.S. degree in Mechanical Engineering from Bucknell University in 2012, and his Ph.D. in Aerospace Engineering at The George Washington University in 2018. His research focusses are in robotic mapping and exploration with range-based sensors, estimation, data association, and flight controls. He has worked on several research projects through the U.S. Air Force Research Laboratory and Naval Research Laboratory.

@@

\noindent{\bf Kuya Takami} is a scientific software developer at Enthought and was a postdoctoral research fellow at the Department of Mechanical and Aerospace Engineering at the George Washington University. He received his doctoral degree in Mechanical Engineering at Virginia Polytechnic Institute and State University in 2015 specializing in robot perception. His main interests include mobile robot perception and autonomous systems.
